OpenMPIR

### 2017-09-07 paper.tex
Continue to respond to comments

While we would like to distinguish between these, it is difficult to do so with
only performance counter information. A more thorough investigation would
require deep knowledge of each of the frontends and runtimes. While the
importance of optimizations of parallel code is clear, we hypothesize that most
of the disparity present in these results is a function of runtime
implementation differences. Our evidence for this comes from Schardl et al.
\cite{tapir}. Generally, the effect of the optimizations that have been
implemented for Tapir IR are outweighed by runtime contention, memory accesses,
etc. for parallel runs. \gsnote{Billy, this OK? Don't want to sound too
negative about the importance of the optimizations you've implemented.}
\wmnote{So actually the memory accesses are happily an optimization Tapir does
-- mainly some mem2reg optimization that may not make much of a different (though still something)
on one core, is a lot more impactful on multicores because of issues regarding contention
forcing a cache line flush.
Also I'm not convinced there wasn't an impact on FFT/nqueens because we did see a
decent improvement from tapir on that -- though I wouldn't be suprised to see the runtime
contribute a large chunk of that.
Fibonacci is certainly runtime based because there's basically no work inside of
it so its almost entirely a measurement of the runtime efficiency.
Sort I'm not sure on depending on the implementation
}

>>>>

While we would like to distinguish between these, it is difficult to do so with
only performance counter information. A more thorough investigation would
require deep knowledge of each of the frontends and runtimes. While the
importance of optimizations of parallel code is clear, we hypothesize that most
of the disparity present in these results is a function of runtime
implementation differences. Our evidence for this comes from Schardl et al.
\cite{tapir}. Generally, the effect of the optimizations that have been
implemented for Tapir IR are outweighed by runtime contention, memory accesses,
etc. for parallel runs. \gsnote{Billy, this OK? Don't want to sound too
negative about the importance of the optimizations you've implemented.}
\wmnote{So actually the memory accesses are happily an optimization Tapir does
-- mainly some mem2reg optimization that may not make much of a different (though still something)
on one core, is a lot more impactful on multicores because of issues regarding contention
forcing a cache line flush.
Also I'm not convinced there wasn't an impact on FFT/nqueens because we did see a
decent improvement from tapir on that -- though I wouldn't be suprised to see the runtime
contribute a large chunk of that, especially for nqueens because that seems like a much
larger improvement than the serial optimizations applied to parallel program alone (when we tested).
Fibonacci is certainly runtime based because there's basically no work inside of
it so its almost entirely a measurement of the runtime efficiency.
Sort I'm not sure on depending on the implementation
}
